Eval expressions

### 2021-01-12 analysis/expressions.Rmd
Expressions with only variable names.

```{r}
arithm_folded %>% group_by(expr_resolved) %>% summarise(n_call_sites = n_distinct(src_ref), n_packages = n_distinct(ev_package)) %>% datatable()
```

@@

>>>>

```{r}
n_arithm_call_sites <- arithm_folded %>% pull(src_ref) %>% n_distinct()

arithm_folded %>% group_by(expr_resolved) %>% summarise(n_call_sites = n_distinct(src_ref), n_packages = n_distinct(ev_package)) %>% datatable()
```

The total number of call sites with those arithmetic on constants is `r n_arithm_call_sites`.

@@

Here, we analyze expressions with only a variable name.

```{r}
with_var <- E %>% filter(str_detect(expr_resolved, "^(?:\\.[:alpha]|[:alpha:])[[:alpha:][:digit:]_\\.]*$"))
```

We can categorize them by number of call sites and number of packages:
```{r}
n_with_var <- with_var %>% pull(src_ref) %>% n_distinct()

with_var %>% group_by(expr_resolved) %>% summarise(n_call_sites = n_distinct(src_ref), n_packages = n_distinct(ev_package)) %>% datatable()
```

There are `r n_with_var` such call sites.
